Urban Crime Dynamics: Trends in Theft and Assault Over 2014 to 2023

### 2024-09-26 paper/paper.qmd
Change the graph 1 analyse and the discussion

@fig-theft-rate-trend-2014-to-2023 shows the trend of theft rates by region from 2014 to 2023. Most of the areas show a relatively stable and low crime rate for a long time, which may prove that the area has a relatively perfect social security management methods and a relatively stable life state. In addition, crime rates in some areas are more variable and generally higher than in others. It is worth noting that between 2017 and 2019, most regions showed a trend of increasing theft rates, which reflects changes in social conditions or economic development at the time. Overall, theft rates remained relatively flat in most areas, with only slight fluctuations. In addition, there are significant differences in the theft rate in different regions at the same time, which may be related to different social conditions in different regions, such as law enforcement, economic status, population distribution and other factors.

@@

Another key point in the discussion is the impact of demographics on theft rates. The @Population-and-attack-rate shows the relationship between theft rates and population in 2023. Although there is no clear linear relationship, it is not difficult to find that communities with larger populations also tend to show higher rates of assault. This is consistent with the emphasis in @bettencourt2007growth: The non-linear relationship between population growth and crime rate indicates that with the expansion of community size, especially the incidence of crimes such as assaults related to social interaction will also increase. However, the data also shows that some areas, despite having smaller populations, also have unusually high attack rates. This could be related to a lack of local law enforcement or social instability. Local police should step up patrols to reduce conflicts. Second, @fig-Bar-chart-2023-theft-rates shows the 20 areas with the highest theft rates in 2023, and it's not hard to find that the spatial distribution of crime shows significant differences across different neighborhoods. The Yonge-Bay Corridor and Yorkdale-Glen Park areas with large population traffic have higher theft rates. By @wang2019spatial Criminal activity is often concentrated in some specific neighborhoods, which is closely related to the socioeconomic status of the community. Here, the view emphasized by @bettencourt2007growth that communities with higher population density usually have higher assault crime rates has also been verified.

>>>>

@fig-theft-rate-trend-2014-to-2023 shows trends in the Top 15 and Bottom 15 Cities by Average Theft Rate from 2014 to 2023. Regardless of the theft rate, most areas show relatively stable crime rate in a long period of time, which may prove that this area has relatively perfect social security management mode and relatively stable life state. In addition, crime rates vary widely in some areas and are generally higher than in others. It is worth noting that between 2019 and 2020, most regions showed a trend of rising theft rates, reflecting changes in social conditions or economic development at the time. Overall, theft rates remained relatively flat in most regions, with only slight fluctuations. In addition, there are significant differences in the theft rate between different regions during the same period, which may be related to different social conditions in different regions, such as law enforcement efforts, economic conditions, population distribution and other factors.

@@

Another key point in the discussion is the impact of demographics on theft rates. The @fig-population-and-assault-rate shows the relationship between theft rates and population in 2023. Although there is no clear linear relationship, it is not difficult to find that communities with larger populations also tend to show higher rates of assault. This is consistent with the emphasis in @bettencourt2007growth: The non-linear relationship between population growth and crime rate indicates that with the expansion of community size, especially the incidence of crimes such as assaults related to social interaction will also increase. However, the data also shows that some areas, despite having smaller populations, also have unusually high attack rates. This could be related to a lack of local law enforcement or social instability. Local police should step up patrols to reduce conflicts. Second, @fig-Bar-chart-2023-theft-rates shows the 20 areas with the highest theft rates in 2023, and it's not hard to find that the spatial distribution of crime shows significant differences across different neighborhoods. The Yonge-Bay Corridor and Yorkdale-Glen Park areas with large population traffic have higher theft rates. By @wang2019spatial Criminal activity is often concentrated in some specific neighborhoods, which is closely related to the socioeconomic status of the community. Here, the view emphasized by @bettencourt2007growth that communities with higher population density usually have higher assault crime rates has also been verified.
